Full title goes here

### 2021-09-13 manuscript/manuscript.Rmd
Add some possible ideas for paper structure

>>>>

Ideas:

- Be like @Rohrer:2018 or @BlackwellGlynn:2018 and focus mostly on the DAG framework + a simulated example + an applied example from 1–2 previously published NVSQ or Voluntas papers - make it not super mathy, but still introduce $\operatorname{do}(\cdot)$ notation (like explain how $P(y \mid \operatorname{do}(x))$ is not the same as the observational $P(y \mid x)$, and that's why correlation ≠ causation)
- …or, be like @BaBerrettCoupet:2021 and show a range of methods, like DAGs, RCTs, diff-in-diff, RD, and IV
- …or do both and focus mostly on DAGs but also include a section that maps traditional econometrics methods to the DAG world?
